True versus apparent shapes of astrophysical bow shocks

### 2016-02-02 papers/Paper1/sec-application.tex
Insert proplyds measurements table
Change \include to \input
\include is only useful for including whole chapters in a very large
document - see
http://tex.stackexchange.com/questions/246/when-should-i-use-input-vs-include
Added references to introduction

We can obtain $R_{90}$ by the following process:
Evaluating equations  (\ref{eq:th1th}) and (23) from \citep{canto:1996} at $\theta=\frac{\pi}{2}$ we obtain the following:

@@

Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta_1^C$. We followed the brightness contours along the 
bow shocks to mark the shell's position. In order to obtain the set of measurements $(R_0, R_c, D)$, we moved to the proplyd's reference frame, (where the proplyd's position)
is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions. The figure ()
shows a representation ofthe metodology described.

%\begin{figure}
%\end{figure}

>>>>

We can obtain $R_{90}$ by the following process:
Evaluating equations  (\ref{eq:th1th}) and (23) from \citep{Canto:1996} at $\theta=\frac{\pi}{2}$ we obtain the following:

@@

Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta_1^C$. We followed the brightness contours along the 
bow shocks to mark the shell's position. In order to obtain the set of measurements $(R_0, R_c, D)$, we moved to the proplyd's reference frame, (where the proplyd's position)
is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions. The figure ()
shows a representation of the metodology described.

\input{proplyds-table}
%\begin{figure}
%\end{figure}

### 2016-02-02 papers/Paper1/sec-intro.tex
Added references to introduction

The archetypical bow shock is formed when a solid body moves
supersonically through a compressible fluid.  Terrestrial examples
include the atmospheric re-entry of a space capsule, or the sonic boom
produced by a supersonic jet \citep{van-Dyke:1982a}.  In astrophysics
the term bow shock is employed more widely, to refer to many different
types of curved shocks that have approximate cylindrical symmetry.

>>>>

The archetypal bow shock is formed when a solid body moves
supersonically through a compressible fluid.  Terrestrial examples
include the atmospheric re-entry of a space capsule, or the sonic boom
produced by a supersonic jet \citep{van-Dyke:1982a}.  In astrophysics
the term bow shock is employed more widely, to refer to many different
types of curved shocks that have approximate cylindrical symmetry.
Instead of a solid body, astrophysical examples usually involve the
interaction of \emph{two} supersonic flows, such as the situation of a
stellar wind emitted by a star that moves supersonically through the
interstellar medium \citep{van-Buren:1988a, Kobulnicky:2010a,
  van-Marle:2011a, Mackey:2012b, Mackey:2015a}.  In such cases, two
shocks are generally produced, one in each flow.  Sometimes,
especially in heliospheric studies \citep{Zank:1999a, Scherer:2014a}, the
term ``bow shock'' is reserved for the shock in the ambient medium,
with the other being called the ``wind shock'' or ``termination
shock''.  However, in other contexts such as colliding wind binaries
\citep{Stevens:1992a, Gayley:2009a} such a distinction is not so
useful.  In this paper we use the term ``bow shock'' in a more general
sense to refer to either of the two shocks, or to the shocked gas in
between them.
